---
title: "Central Limit Theorem"
author: "D"
date: "26 dicembre 2015"
output: html_document
---
1. Perfect coin P(X = 0) = P(H) = 0.5 = p, P(X = 1) = P(T) = 0.5
```{r}
rm(list = ls())

N = 1000 # Num of coin toss
p = 0.5

```
E[x] = sum_i_1_2 X_i*P(X = x_i) = P(X = 0)*(1 - 0.5)  + P(X = 1)*0.5 = P(H)*p + P(T)*0.5 = 0*0.5 + 1*0.5 = 0.5
```{r}
E_X = 0*0.5 + 1*0.5

```

VAR(X) = E[(x - E[x])^2]:
```{r}
VAR_X = (0 - E_X)^2*(1 - p) + (1 - E_X)^2*p

```

2. Compute probability that in N coin toss the number of heads will not be greather than MAX_HEADS = 549. Each coin toss is X_i; X_i are random variables:
1. independent
2. with same distribution
3. with mean m = 0.5 and variance sigma_2 = 0.24

Compute probability that in N = 1000 coin toss we do not get more than 549 Heads
```{r}
#rm(list = ls())

N = 1000
MAX_HEADS = 549
x_star = (549 - N*E_X)/(sqrt(N)*sqrt(VAR_X))
x_star
x = seq(-10, +10, length = 100)
y = dnorm(x, 0, 1)
plot(x, y, pch = 19, col = "red")
lines(x, y, col = "red", lwd = 2)
arrows(x_star, 0.25, x_star, 0, lwd = 3,  col = "blue")

P_min_star = pnorm(x_star, 0, 1)
P_min_star
```

3. A random number generator produces 50 random nubbers.
What's the probability that the sum lies between 20 and 30?
Each generation is a random variabile
1. independent
2. equally distributed
3. distribution is uniform between 0 and 1
4. mean = 1/2 0 0.5; Var = 1/12
```{r}
N = 50
E_x = 1/2
VAR_X = 1/12
min = 20
max = 30
min_star = (min - N*E_X)/(sqrt(N)*sqrt(VAR_X))
max_star = (max - N*E_X)/(sqrt(N)*sqrt(VAR_X))

P_min_star = pnorm(min_star, 0, 1)
P_max_star = pnorm(max_star, 0, 1)

x = seq(-5, +5, length = 100)
y = dnorm(x, 0, 1)
plot(x, y, pch = 19, col = "red")
lines(x, y, col = "red", lwd = 2)
arrows(min_star, 0.25, min_star, 0, lwd = 3,  col = "blue")
arrows(max_star, 0.25, max_star, 0, lwd = 3,  col = "blue")

P_max_star - P_min_star
```


4. In a class of 30 students average of past tests is 6.2 and standard deviation = 2.5. Compute the probability that next test average will lie between 6 and 6.3
Average is S_30 = SUM_i_1_30 X_i, X_i mark of each student
X_i are
1. independent
2. equally distributed
3. having mean 6.2 and standard deviation 2.5
Need to compute P(6.0 <= S_n/30 <= 6.2)
```{r}
rm(list = ls())
N = 30
E_X = 6.2
VAR_X = 2.5^2

min_ave = 6.0
max_ave = 6.3

min_S_n = min_ave*30
max_S_n = max_ave*30

# get the standard
min_S_n_star = (min_S_n - N*E_X)/(sqrt(N)*sqrt(VAR_X))
max_S_n_star = (max_S_n - N*E_X)/(sqrt(N)*sqrt(VAR_X))

P_min_star = pnorm(min_S_n_star, 0, 1)
P_min_star
P_max_star = pnorm(max_S_n_star, 0, 1)
P_max_star

x = seq(-2, +2, length = 100)
y = dnorm(x, 0, 1)
plot(x, y, pch = 19, col = "red")
lines(x, y, col = "red", lwd = 2)
arrows(min_S_n_star, 0.25, min_S_n_star, min(y), lwd = 3,  col = "blue")
arrows(max_S_n_star, 0.25, max_S_n_star, min(y), lwd = 3,  col = "blue")

P_max_star - P_min_star

```
