---
title: "Central Limit Theorem"
author: "D"
date: "26 dicembre 2015"
output: html_document
---
1. Perfect coin P(X = 0) = P(H) = 0.5 = p, P(X = 1) = P(T) = 0.5
```{r}
rm(list = ls())

N = 1000 # Num of coin toss
p = 0.5

```
E[x] = sum_i_1_2 X_i*P(X = x_i) = P(X = 0)*(1 - 0.5)  + P(X = 1)*0.5 = P(H)*p + P(T)*0.5 = 0*0.5 + 1*0.5 = 0.5
```{r}
E_X = 0*0.5 + 1*0.5

```

VAR(X) = E[(x - E[x])^2]:
```{r}
VAR_X = (0 - E_X)^2*(1 - p) + (1 - E_X)^2*p

```

2. Compute probability that in N coin toss the number of heads will not be greather than MAX_HEADS = 549. Each coin toss is X_i; X_i are random variables:
1. independent
2. with same distribution
3. with mean m = 0.5 and variance sigma_2 = 0.24

Compute probability that in N = 1000 coin toss we do not get more than 549 Heads
```{r}
#rm(list = ls())

N = 1000
MAX_HEADS = 549
x_star = (549 - N*E_X)/(sqrt(N)*sqrt(VAR_X))
x_star
x = seq(-10, +10, length = 100)
y = dnorm(x, 0, 1)
plot(x, y, pch = 19, col = "red")
lines(x, y, col = "red", lwd = 2)
arrows(x_star, 0.25, x_star, 0, lwd = 3,  col = "blue")

P_min_star = pnorm(x_star, 0, 1)
P_min_star
```

3. A random number generator produces 50 random nubbers.
What's the probability that the sum lies between 20 and 30?
Each generation is a random variabile
1. independent
2. equally distributed
3. distribution is uniform between 0 and 1
4. mean = 1/2 0 0.5; Var = 1/12
```{r}
N = 50
E_x = 1/2
VAR_X = 1/12
min = 20
max = 30
min_star = (min - N*E_X)/(sqrt(N)*sqrt(VAR_X))
max_star = (max - N*E_X)/(sqrt(N)*sqrt(VAR_X))

P_min_star = pnorm(min_star, 0, 1)
P_max_star = pnorm(max_star, 0, 1)

x = seq(-5, +5, length = 100)
y = dnorm(x, 0, 1)
plot(x, y, pch = 19, col = "red")
lines(x, y, col = "red", lwd = 2)
arrows(min_star, 0.25, min_star, 0, lwd = 3,  col = "blue")
arrows(max_star, 0.25, max_star, 0, lwd = 3,  col = "blue")

P_max_star - P_min_star
```


4. In a class of 30 students average of past tests is 6.2 and standard deviation = 2.5. Compute the probability that next test average will lie between 6 and 6.3
Average is S_30 = SUM_i_1_30 X_i, X_i mark of each student
X_i are
1. independent
2. equally distributed
3. having mean 6.2 and standard deviation 2.5
Need to compute P(6.0 <= S_n/30 <= 6.2)
```{r}
rm(list = ls())
N = 30
E_X = 6.2
VAR_X = 2.5^2

min_ave = 6.0
max_ave = 6.3

min_S_n = min_ave*30
max_S_n = max_ave*30

# get the standard
min_S_n_star = (min_S_n - N*E_X)/(sqrt(N)*sqrt(VAR_X))
max_S_n_star = (max_S_n - N*E_X)/(sqrt(N)*sqrt(VAR_X))

P_min_star = pnorm(min_S_n_star, 0, 1)
P_min_star
P_max_star = pnorm(max_S_n_star, 0, 1)
P_max_star

x = seq(-2, +2, length = 100)
y = dnorm(x, 0, 1)
plot(x, y, pch = 19, col = "red")
lines(x, y, col = "red", lwd = 2)
arrows(min_S_n_star, 0.25, min_S_n_star, min(y), lwd = 3,  col = "blue")
arrows(max_S_n_star, 0.25, max_S_n_star, min(y), lwd = 3,  col = "blue")

P_max_star - P_min_star

```

5. Compute probability that in N=120 tosse sof a fair coin, the number of heads is between 48 and 72

X_i =p  one toss of the fair coin
E_X = 1/2 = 0.5
VAR_x = 1/4
S_N = SUM_i_1_N X_i

```{r}
rm(list = ls())
N = 120
E_X = 1/2
VAR_X = 1/4

min_S_N = 48
max_S_N = 72

min_S_N_star = (min_S_N - N*E_X)/(sqrt(N)*sqrt(VAR_X))
max_S_N_star = (max_S_N - N*E_X)/(sqrt(N)*sqrt(VAR_X))

P_min_S_N_star = pnorm(min_S_N_star, 0, 1)
P_max_S_N_star = pnorm(max_S_N_star, 0, 1)

P_max_S_N_star - P_min_S_N_star

x = seq(min_S_N_star-2*sqrt(VAR_X), max_S_N_star+2*sqrt(VAR_X), length = 100)
y = dnorm(x, 0, 1)
plot(x, y, pch = 19, col = "red")
lines(x, y, col = "red", lwd = 2)
arrows(min_S_N_star, 0.25, min_S_N_star, min(y), lwd = 3,  col = "blue")
arrows(max_S_N_star, 0.25, max_S_N_star, min(y), lwd = 3,  col = "blue")

```

N = 200 tosses of perfect fair die. What's the probability that an even face will show up between 95 and 105 times
```{r}
rm(list = ls())

N = 200
p = 1/2
faces = c(0, 1) # even face, odd face
E_X = sum(faces)*p
VAR_X = sum((faces - E_X)^2)/length(faces)

min_S_N = 95
max_S_N = 105

min_S_N_star = (min_S_N - N*E_X)/(sqrt(N)*sqrt(VAR_X))
max_S_N_star = (max_S_N - N*E_X)/(sqrt(N)*sqrt(VAR_X))

P_min_S_N_star = pnorm(min_S_N_star, 0, 1)
P_max_S_N_star = pnorm(max_S_N_star, 0, 1)

P_max_S_N_star - P_min_S_N_star

x = seq(min_S_N_star-2*sqrt(VAR_X), max_S_N_star+2*sqrt(VAR_X), length = 100)
y = dnorm(x, 0, 1)
plot(x, y, pch = 19, col = "red")
lines(x, y, col = "red", lwd = 2)
arrows(min_S_N_star, 0.25, min_S_N_star, min(y), lwd = 3,  col = "blue")
arrows(max_S_N_star, 0.25, max_S_N_star, min(y), lwd = 3,  col = "blue")

```

```{r}
rm(list = ls())

N = 500
p = c(1/10, 9/10)
x_i = c(0, 1)
E_X = crossprod(p, x_i) # inner product
VAR_X = sum((x_i - E_X)^2)/length(x_i)

min_S_N = 50
max_S_N = 55

min_S_N_star = (min_S_N - N*E_X)/(sqrt(N)*sqrt(VAR_X))
max_S_N_star = (max_S_N - N*E_X)/(sqrt(N)*sqrt(VAR_X))


```

Dice rolling
```{r}
s = c()
for (i in 1:1000) {
  sample = sample(1:6, 200, replace = TRUE, prob = rep(1/6, 6))
  s = append(s, sum(sample))
}
plot(s)
hist(s, breaks = 100, col = "light blue")


```


Coin tosses
```{r}
rm(list = ls())
p = 0.5 # This is a fair coin
N = 100000 # Number of tosses

# use sample to sample from a vector (sample space)
v = c()
for (i in 1:1000) {
  s = cumsum(sample(c(-1, 1), size = N, replace = TRUE, prob = c(p, 1-p)))
  #print(s)
  v[i] = s[length(s)]
}
hist(v, breaks=100)

v = c()
for (i in 1:1000) {
  s = sum(sample(c(0, 1), size = N, replace = TRUE, prob = c(p, 1-p)))
  #print(s)
  v[i] = s
}
hist(v, breaks=100, col = "light blue")

# use rbinom to draw a number from a Bernoulli distribution
rbinom(n = 1, size = N, prob = p)

```

```{r}
#Material taken from: http://www.rfortraders.com/simulation-of-a-coin-toss-in-r/
  
 # Create an empty list to store the results
 results <- list()
 for(i in 1:10000) {
     coinTosses   <- cumsum(sample(c(-1,1), 1000, replace = TRUE)) 
     results[[i]] <- coinTosses[length(coinTosses)]
 }
 
 # Unlist the list and create a histogram. Set a title and set the color and breaks
hist(unlist(results), main = "Histogram of all the final p&l's",col = "lightblue", breaks = 100)
 
 # Place a vertical line at 0 with a width of 2 in order to show the average of the distribution
 abline(v = 0, col = "red", lwd = 2)
```

