---
title: "Estimating the Parameters of Beta Distribution"
author: "D"
date: "Jan 8th, 2017"
output: html_document
---
This is from:
http://stats.stackexchange.com/questions/12232/calculating-the-parameters-of-a-beta-distribution-using-the-mean-and-variance

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
rm(list=ls())

```

mu and var (i.e. sigma^2) are the mean and the variance of the final beta distribution. How do I compute the alpha nad beta paramters generatng the beta?

alpha and beta are related to mu and variance via the relations:

mu = alpha/(alpha+beta)
variance = alpha*beta/((alpha+beta^2)*(alpha+beta+1))

Inverting these relations gives;

alpha = ((1-mu)/variance) - 1/mu)*mu^2
beta = alpha*(1/mu -1)
#beta = ((1-mu)/variance) - 1/mu)*mu*(1-mu)

Can use this function:
```{r}
estBetaParams <- function(mu, variance) {
  alpha <- ((1 - mu) / variance - 1 / mu) * mu ^ 2
  beta <- alpha * (1 / mu - 1)
  return(params = list(alpha = alpha, beta = beta))
}

```

For example, I want a beta-distribution having mean mu=0.27 and variance var=0.324. The parameters are:
```{r}
mu=0.27
variance=0.0324
betas <- estBetaParams(mu, variance)
betas
```

```{r}
alpha <- betas$alpha
beta <- betas$beta
mu_check = alpha/(alpha+beta)
mu_check
variance_check = alpha*beta/((alpha+beta)^2*(alpha+beta+1))
variance_check

abs(mu-mu_check)<1E-4
abs(variance-variance_check)<1E-4
```

```{r}
sample=rbeta(1E6, shape1=betas$alpha, shape2=betas$beta)
mean(sample)
var(sample)
```

```{r}
x=1:100/100
y=dbeta(x, shape1=betas$alpha, shape2=betas$beta)
par(mfrow=c(2,1))
plot(x, y)
y=pbeta(x, shape1=betas$alpha, shape2=betas$beta)
plot(x, y)

```

